The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-07-24 paper.tex
Started on 3C section

>>>>

The patterns of epenthesis are as follows.

If C\textsubscript{2}-C\textsubscript{3} rises by two or more sonority steps,
the only possible output is [CC\textipa{1}C].

\ex. \a. \textipa{j@gd1ro}, *\textipa{j@g1dro} `let them put to bed'
%TODO : convert the rest to actual words
%TODO : check why I claim this has no variation even though it's underlined

If C\textsubscript{2}-C\textsubscript{3} is of level sonority or rises by
a single sonority step, the primary form is [CC\textipa{1}C], but [C\textipa{1}CC]
is also possible.

\ex. \a. /sgd/ $\rightarrow$ [sg\iep d] preferred, [s\iep gd] possible
     \b. /gdf/ $\rightarrow$ [gd\iep f] preferred, [g\iep df] possible

If C\textsubscript{2} is /r/ and C\textsubscript{3} is a sonorant, the primary
form is [C\textipa{1}CC], but [CC\textipa{1}C] is also possible.

\ex. \a. /krm/ $\rightarrow$ [k'\iep rm] preferred, [k'r\iep m] also possible

If C\textsubscript{1} is /r/ or /n/ and the verbal form is jussive, 
always epenthesise as [CC\textipa{1}C]. This is due to a
morphophonological constraint on Chaha jussives.

Otherwise (if C\textsubscript{2}-C\textsubscript{3} is of falling sonority and 
C\textsubscript{2} is not /r/), [C\textipa{1}CC] is the only possible outcome.
\ex. \a. /mrg/ $\rightarrow$ m\iep rg, *mr\iep g
     \b. TODO

There is a single exception to the previous generalisation: Rose reports that /mst/
epenthesises as [ms\textipa{1}t]. Another native speaker reports that
         he epenthesises this as [m\textipa{1}st] (Degif Petros Banksira, p.c.)
